Imputation of Incomplete Multilevel Data with R

### 2024-01-08 Manuscript/manuscript.qmd
small textual change in intro

This tutorial is dedicated to readers who are unfamiliar with multiple imputation. More experienced readers can skip the introduction (case study 1) and directly head to practical applications of multilevel imputation under MAR conditions (case study 2) or under MNAR conditions (case study 3).

>>>>

This tutorial is dedicated to readers who are unfamiliar with multiple imputation. More experienced readers can skip the remainder of the introduction section, background section and case study 1, and directly head to practical applications of multilevel imputation under MAR conditions (case study 2) or under MNAR conditions (case study 3).
